Fixing Vulnerabilities Hinders Maintainability

### 2019-02-05 paper/ICPC19/icpc19.tex
some more fixes

Other studies investigated the effect of programming languages in software
quality~\cite{Ray:2014:LSS:2635868.2635922,Ray:2017:LSP:3144574.3126905}. The first
study shows that some programming languages are more buggy than others, i.e.,
language design has an impact on software quality. However, the authors of the
second study were not able to reproduce the first one and did not obtain any
evidence about the impact of language design. Both have used the number of
defects as an indicator of software quality. In addition,
Berger et al. ($2019$)~\cite{2019arXiv190110220B} tried to reproduce~\cite{Ray:2014:LSS:2635868.2635922,
Ray:2017:LSP:3144574.3126905} and identified flaws that throw into distrust the previously demonstrated
correlation between programming language and software defects. Our works studies how
security refactorings affect software quality based on the code maintainability
analysis and provides evidence that programming language have impact on
maintainability.

>>>>

There are studies that investigated the impact of programming languages on software
quality~\cite{Ray:2014:LSS:2635868.2635922,Ray:2017:LSP:3144574.3126905}. The first
study shows that some programming languages are more buggy-prone than others. However,
the authors of the second study were not able to reproduce it, not obtaining any
evidence about the impact of language design. Both have used the number of
defects as an indicator of software quality. In addition,
Berger et al. ($2019$)~\cite{2019arXiv190110220B} tried to reproduce~\cite{Ray:2014:LSS:2635868.2635922,
Ray:2017:LSP:3144574.3126905} and identified flaws that throw into distrust the previously demonstrated
correlation between programming language and software defects. Our works studies how
security refactorings affect software quality based on the code maintainability
analysis and provides evidence that programming language have impact on
maintainability.
